Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}

### 2019-04-13 manuscript.tex
drop bms examples; update and expand SI

\noindent These examples make clear that despite the \textit{causal} inference potentially provided by the AMCE, the quantity of interest is frequently used to provide a characterization of a preferences that has a distinctly descriptive flavor about the relative \textit{levels} of support across profiles and also across subgroups of respondents. Indeed, this style of description is widespread in conjoint analyses. This use of conjoints to provide descriptive inferences about patterns of preferences is important because AMCEs are defined as \textit{relative} quantities, requiring that patterns of preferences are expressed against a baseline, reference category for each conjoint feature. A positive AMCE is read as higher favorability but it is only higher relative to whatever category serves as the baseline. For example, in the \citeauthor{HainmuellerHopkinsYamamoto2014} candidate example, choosing a non-religious candidate as a baseline and interpreting the resulting AMCES means that the differences between other pairs of marginal means (e.g., evaluations of Mormon and Evangelical candidates) are not obvious. The negative direction, and the size, of the AMCEs for Mormon and Evangelical candidates would be different if the least-liked category of Mormons were the reference group. More trivially, \citet{TeeleKallaRosenbluth2018} describe their comparisons about public preferences for female candidates relative to male candidates, but could have equivalent described patterns of equal size but opposite sign comparing preferences over male relative to female candidates.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
\includegraphics[width=\maxwidth]{figure/reference_category-1} \caption[Estimated AMCEs for Levels of the `Education' Feature for Each Possible Reference Category from Hainmueller et al.'s (2014) Immigration Experiment]{Estimated AMCEs for Levels of the `Education' Feature for Each Possible Reference Category from Hainmueller et al.'s (2014) Immigration Experiment}\label{fig:reference_category}
\end{figure}

Though seemingly arbitrary, the choice of reference category for estimating AMCEs can be quite consequential.\footnote{Since this manuscript has been under review, we have been made aware of one working paper by \citet{ClaytonFerwerdaHoriuchi2018}, on the topic of immigration preferences, that correctly notes the need to address the arbitrary reference category in order to compare subgroup preferences.} For example, in \citeauthor{HainmuellerHopkinsYamamoto2014}'s candidate experiment (again, see \ref{fig:hainmueller_candidate_replication}), the least liked education level (``no formal education'') is chosen as a reference category, but the authors could have presented the results using any of the categories as the baseline. Figure \ref{fig:reference_category} shows how the estimated AMCEs for each level of the education feature would have differed depending on that choice. Selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), makes some AMCEs positive and others negative but all AMCEs can be made positive (or negative) simply by choosing a different baseline. The results would be numerically equivalent --- the alternative linear models used to the estimate the AMCEs have a mathematical equivalence --- but the choice has sizeable consequences for the interpretation of conjoint analyses, as we discuss below.\footnote{In \textit{constrained} conjoint designs, the choice of reference category is even more important. Consider, for example, the design of \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, which constrains the ``Country of Origin`` feature so that levels `India,' `Germany,' `France,' `Mexico,' `Philippines,' and `Poland' cannot co-occur with the `Escape Persecution' level of the ``Reason for Application'' feature. Consequently, the AMCE for the ``Escape Persecution'' level (relative to the  ``Reunite with family'' reference category) is only defined for the subset of the design involving countries `China,' `Sudan,' `Somalia,' and `Iraq.' The AMCEs for those four countries (relative to India as a baseline) marginalize across all reasons for application, but the AMCEs for the first six countries marginalize only across the latter two reasons. Thus the interpretation of AMCEs --- and the basic ability to estimate them in constrained designs --- depends entirely upon the selection of a reference category where all feature levels can co-occur. In a design where \textit{all} features are constrained, then AMCEs are undefined for the design as a whole and only estimable for subsets of the design that are \textit{conditionally} unconstrained.}

%To demonstrate this, Figure \ref{fig:reference_category} shows the estimated AMCEs for the country of origin feature from \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, with the analysis repeated ten times each time using a different country as the reference category. For example, the top-most set of points and error bars convey the AMCE for Iraq from each of these analyses. When Iraq is the reference category, its AMCE is undefined. When any other country is chosen as a reference category, the AMCE for Iraq is negative because respondents are more negative toward Iraqi immigrants than they are toward those of other countries. Similarly, the bottom set of points and error bars reflects the estimated AMCEs for Germany. When Germany is the reference category, its AMCE is undefined but when any other country is used as the reference category, its AMCE is positive.

%These cases are therefore not \textit{directionally} sensitive to the choice of reference category but of course the point estimates vary considerably. But the estimated AMCE of countries who are neither strongly disliked or strongly favored by respondents are highly sensitive to choice of reference category. Consider, for example, the estimated AMCEs for China (the four set of points from the top). When highly disliked countries are chosen as the reference category (like Somalia, Sudan, or Iraq), the AMCE for China is positive; when highly favored countries are chosen (like Germany, Poland, or the Philippines), the AMCE for China is negative.

@@

To draw this example out more fully, the upper panel of Figure \ref{fig:tkr_replication} shows AMCEs for \citeauthor{TeeleKallaRosenbluth2018}'s candidate choice experiment for the full sample of respondents. The second panel shows full sample marginal means. Respondents' preference for female candidates is very apparent in both forms of analysis in the upper two panels because the AMCE definitionally equals the difference in marginal means. But how do Republicans and Democrats differ in their preferences over male and female candidates? The third panel shows conditional AMCEs separately for Democratic and Republican voters, as provided in the original paper and the lower panel shows the results using conditional marginal means for Democratic and Republican voters.\footnote{We opt here for visual presentation of results; tabular presentation of AMCEs, marginal means, and associated standard errors for all examples are included in the Appendix.} By requiring a reference category fixed to zero, the conditional AMCE results in the third panel suggest that there is a very large difference in favorability toward female candidates between Republican and Democratic respondents. In reality, however, the difference in these conditional AMCEs (0.086) reflects the true difference in favorability toward female candidates (difference: 0.045; Democrats: 0.537, Republicans: 0.492) \textit{plus} the difference in favorability toward male candidates (difference: 0.045; Democrats: 0.463, Republicans: 0.508). Because Democrats and Republicans actually differ in their views of profiles containing the reference (male) category, AMCEs sum the true differences in preferences for a given feature level with the difference in preferences toward the reference category.\footnote{Another example that clearly demonstrates the discrepancy between the differences in preferences and the differences in conditional AMCEs can be seen very clearly in the ``political experience'' feature of this experiment (see Supporting Materials). The conditional AMCEs correctly convey that both Democrats and Republicans are more likely to favor experienced than inexperienced candidates. Reading the AMCEs descriptively, however, would suggest that Democratic voters are more favorable toward candidates with all levels of experience compared to Republican voters (i.e., Republicans and Democrats differ in their preferences over experienced candidates). In reality, however, the conditional marginal means reveal that actually Democrats and Republicans have very similar preferences toward candidates with 1 or 3 years of experience, but differ dramatically in their preferences over candidates with no experience (the reference category) and those with 8 years experience. Democrats are much more sensitive to experience than are Republicans and important differences in preferences between the groups are apparent for very high and very low experience, but the conditional AMCEs suggest that preferences differ at all levels of experience, when in reality they do not.}

@@

@@

\subsection{Subgroup Analysis for Hainmueller et al. (2014) Immigration Experiment using AMCEs}

@@

\subsection{Subgroup Analysis for Hainmueller et al. (2014) Immigration Experiment using MMs}

@@

\section{Ballard-Rosa et al. (2016) Tax Preference Experiment}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/bms_amce_appendix-1}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Sun Nov 25 10:42:47 2018
\begin{table}[ht]
\centering
\begin{tabular}{lp{1.5in}rrr}
  \hline
feature & level & estimate & std.error & z \\ 
  \hline
Tax rate for $<$\$10,000 & $<$10k: 0\% & 0.00 &  &  \\ 
  Tax rate for $<$\$10,000 & $<$10k: 5\% & -0.02 & 0.01 & -3.81 \\ 
  Tax rate for $<$\$10,000 & $<$10k: 15\% & -0.11 & 0.01 & -15.97 \\ 
  Tax rate for $<$\$10,000 & $<$10k: 25\% & -0.24 & 0.01 & -28.33 \\ 
  Tax rate for \$10,000-\$35,000 & 10-35k: 5\% & 0.00 &  &  \\ 
  Tax rate for \$10,000-\$35,000 & 10-35k: 15\% & -0.02 & 0.01 & -2.94 \\ 
  Tax rate for \$10,000-\$35,000 & 10-35k: 25\% & -0.10 & 0.01 & -9.42 \\ 
  Tax rate for \$10,000-\$35,000 & 10-35k: 35\% & -0.22 & 0.01 & -15.96 \\ 
  Tax rate for \$25,000-\$85,000 & 35-85k: 5\% & 0.00 &  &  \\ 
  Tax rate for \$25,000-\$85,000 & 35-85k: 15\% & 0.00 & 0.01 & 0.03 \\ 
  Tax rate for \$25,000-\$85,000 & 35-85k: 25\% & -0.07 & 0.01 & -9.18 \\ 
  Tax rate for \$25,000-\$85,000 & 35-85k: 35\% & -0.13 & 0.01 & -14.55 \\ 
  Tax rate for \$85,000-\$175,000 & 85-175k: 5\% & 0.00 &  &  \\ 
  Tax rate for \$85,000-\$175,000 & 85-175k: 15\% & 0.01 & 0.01 & 2.06 \\ 
  Tax rate for \$85,000-\$175,000 & 85-175k: 25\% & -0.02 & 0.01 & -2.80 \\ 
  Tax rate for \$85,000-\$175,000 & 85-175k: 35\% & -0.01 & 0.01 & -2.19 \\ 
  Tax rate for \$175,000-\$375,000 & 175-375k: 5\% & 0.00 &  &  \\ 
  Tax rate for \$175,000-\$375,000 & 175-375k: 15\% & 0.03 & 0.01 & 5.97 \\ 
  Tax rate for \$175,000-\$375,000 & 175-375k: 25\% & 0.04 & 0.01 & 6.53 \\ 
  Tax rate for \$175,000-\$375,000 & 175-375k: 35\% & 0.06 & 0.01 & 9.77 \\ 
  Tax rate for \$175,000-\$375,000 & 175-375k: 45\% & 0.03 & 0.01 & 4.80 \\ 
  Tax rate for $>$\$375,000 & $>$375k: 5\% & 0.00 &  &  \\ 
  Tax rate for $>$\$375,000 & $>$375k: 15\% & 0.06 & 0.01 & 8.22 \\ 
  Tax rate for $>$\$375,000 & $>$375k: 25\% & 0.09 & 0.01 & 12.18 \\ 
  Tax rate for $>$\$375,000 & $>$375k: 35\% & 0.11 & 0.01 & 15.44 \\ 
  Tax rate for $>$\$375,000 & $>$375k: 45\% & 0.11 & 0.01 & 13.23 \\ 
  Tax rate for $>$\$375,000 & $>$375k: 55\% & 0.08 & 0.01 & 9.55 \\ 
  Tax revenue & $<$75\% & 0.00 &  &  \\ 
  Tax revenue & 75-95\% & 0.03 & 0.01 & 3.56 \\ 
  Tax revenue & 95-105\% & 0.07 & 0.01 & 6.11 \\ 
  Tax revenue & 105-125\% & 0.09 & 0.01 & 6.33 \\ 
  Tax revenue & $>$125\% & 0.14 & 0.02 & 7.22 \\ 
   \hline
\end{tabular}
\end{table}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/bms_mm_appendix-1}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Sun Nov 25 10:42:56 2018
\begin{table}[ht]
\centering
\begin{tabular}{lp{1.5in}rrr}
  \hline
feature & level & estimate & std.error & z \\ 
  \hline
Tax rate for $<$\$10,000 & $<$10k: 0\% & 0.57 & 0.01 & 9.37 \\ 
  Tax rate for $<$\$10,000 & $<$10k: 5\% & 0.56 & 0.01 & 8.06 \\ 
  Tax rate for $<$\$10,000 & $<$10k: 15\% & 0.49 & 0.01 & -1.11 \\ 
  Tax rate for $<$\$10,000 & $<$10k: 25\% & 0.37 & 0.01 & -16.07 \\ 
  Tax rate for \$10,000-\$35,000 & 10-35k: 5\% & 0.54 & 0.01 & 4.75 \\ 
  Tax rate for \$10,000-\$35,000 & 10-35k: 15\% & 0.54 & 0.01 & 5.55 \\ 
  Tax rate for \$10,000-\$35,000 & 10-35k: 25\% & 0.50 & 0.01 & 0.39 \\ 
  Tax rate for \$10,000-\$35,000 & 10-35k: 35\% & 0.42 & 0.01 & -10.62 \\ 
  Tax rate for \$25,000-\$85,000 & 35-85k: 5\% & 0.53 & 0.01 & 3.45 \\ 
  Tax rate for \$25,000-\$85,000 & 35-85k: 15\% & 0.54 & 0.01 & 5.37 \\ 
  Tax rate for \$25,000-\$85,000 & 35-85k: 25\% & 0.49 & 0.01 & -1.27 \\ 
  Tax rate for \$25,000-\$85,000 & 35-85k: 35\% & 0.44 & 0.01 & -7.50 \\ 
  Tax rate for \$85,000-\$175,000 & 85-175k: 5\% & 0.50 & 0.01 & 0.00 \\ 
  Tax rate for \$85,000-\$175,000 & 85-175k: 15\% & 0.51 & 0.01 & 1.42 \\ 
  Tax rate for \$85,000-\$175,000 & 85-175k: 25\% & 0.49 & 0.01 & -1.00 \\ 
  Tax rate for \$85,000-\$175,000 & 85-175k: 35\% & 0.50 & 0.01 & -0.46 \\ 
  Tax rate for \$175,000-\$375,000 & 175-375k: 5\% & 0.46 & 0.01 & -4.37 \\ 
  Tax rate for \$175,000-\$375,000 & 175-375k: 15\% & 0.50 & 0.01 & -0.47 \\ 
  Tax rate for \$175,000-\$375,000 & 175-375k: 25\% & 0.51 & 0.01 & 0.84 \\ 
  Tax rate for \$175,000-\$375,000 & 175-375k: 35\% & 0.53 & 0.01 & 3.11 \\ 
  Tax rate for \$175,000-\$375,000 & 175-375k: 45\% & 0.51 & 0.01 & 0.80 \\ 
  Tax rate for $>$\$375,000 & $>$375k: 5\% & 0.41 & 0.01 & -9.57 \\ 
  Tax rate for $>$\$375,000 & $>$375k: 15\% & 0.47 & 0.01 & -3.30 \\ 
  Tax rate for $>$\$375,000 & $>$375k: 25\% & 0.51 & 0.01 & 0.97 \\ 
  Tax rate for $>$\$375,000 & $>$375k: 35\% & 0.54 & 0.01 & 4.48 \\ 
  Tax rate for $>$\$375,000 & $>$375k: 45\% & 0.55 & 0.01 & 4.75 \\ 
  Tax rate for $>$\$375,000 & $>$375k: 55\% & 0.53 & 0.01 & 3.12 \\ 
  Tax revenue & $<$75\% & 0.57 & 0.01 & 8.22 \\ 
  Tax revenue & 75-95\% & 0.53 & 0.01 & 3.47 \\ 
  Tax revenue & 95-105\% & 0.51 & 0.01 & 1.18 \\ 
  Tax revenue & 105-125\% & 0.48 & 0.01 & -2.21 \\ 
  Tax revenue & $>$125\% & 0.41 & 0.01 & -10.54 \\ 
   \hline
\end{tabular}
\end{table}

\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by ``Taxes Harm Economy'' Split using AMCEs}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/bms_subgroup_amce_appendix1-1}

\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by ``Taxes Harm Economy'' Split using MMs}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/bms_subgroup_mm_appendix1-1}

\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by Inequity Aversion using AMCEs}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/bms_subgroup_amce_appendix2-1}

\subsection{Subgroup Analysis for Ballard-Rosa et al. (2016), by Inequity Aversion using MMs}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/bms_subgroup_mm_appendix2-1}

\subsection{Comparison of Alternative Reference Categories for Ballard-Rosa et al. (2016) Tax Preference Experiment, by ``Taxes Harm Economy'' Split}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/bms_subgroup_example_plot1-1}

\subsection{Comparison of Alternative Reference Categories for Ballard-Rosa et al. (2016) Tax Preference Experiment, by Inequity Aversion}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/bms_subgroup_example_plot2-1}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
##      outcome statistic                                 feature
## 1  choice_cj      amce    Costs to average household per month
## 2  choice_cj      amce    Costs to average household per month
## 3  choice_cj      amce    Costs to average household per month
## 4  choice_cj      amce    Costs to average household per month
## 5  choice_cj      amce    Costs to average household per month
## 6  choice_cj      amce                   Distribution of costs
## 7  choice_cj      amce                   Distribution of costs
## 8  choice_cj      amce                   Distribution of costs
## 9  choice_cj      amce                   Distribution of costs
## 10 choice_cj      amce       Number of participating countries
## 11 choice_cj      amce       Number of participating countries
## 12 choice_cj      amce       Number of participating countries
## 13 choice_cj      amce   Share of global emissions represented
## 14 choice_cj      amce   Share of global emissions represented
## 15 choice_cj      amce   Share of global emissions represented
## 16 choice_cj      amce Sanctions for missing reduction targets
## 17 choice_cj      amce Sanctions for missing reduction targets
## 18 choice_cj      amce Sanctions for missing reduction targets
## 19 choice_cj      amce Sanctions for missing reduction targets
## 20 choice_cj      amce                           Monitoring by
## 21 choice_cj      amce                           Monitoring by
## 22 choice_cj      amce                           Monitoring by
## 23 choice_cj      amce                           Monitoring by
##                                level     estimate   std.error           z
## 1                      \20028 per month  0.000000000          NA          NA
## 2                      \20056 per month -0.097845284 0.001402351  -69.772319
## 3                      \20084 per month -0.170008434 0.001468627 -115.760108
## 4                     \200113 per month -0.263769273 0.001471840 -179.210616
## 5                     \200141 per month -0.332856845 0.001422455 -234.001744
## 6                          Only rich  0.000000000          NA          NA
## 7         Prop. to current emissions  0.065924582 0.001340698   49.171839
## 8      Prop. to history of emissions  0.052479783 0.001345106   39.015350
## 9  Rich pay more than poor countries  0.057280714 0.001327647   43.144545
## 10                         20 of 192  0.000000000          NA          NA
## 11                         80 of 192  0.092728950 0.001141542   81.231296
## 12                        160 of 192  0.156435103 0.001175080  133.127175
## 13          40% of current emissions  0.000000000          NA          NA
## 14          60% of current emissions  0.022498908 0.001117762   20.128532
## 15          80% of current emissions  0.045174103 0.001125637   40.132047
## 16                              None  0.000000000          NA          NA
## 17               \2006 per hh and month  0.028464249 0.001308130   21.759490
## 18              \20017 per hh and month -0.018533001 0.001326110  -13.975465
## 19              \20023 per hh and month -0.053180963 0.001312140  -40.529947
## 20                   Your government  0.000000000          NA          NA
## 21                 Indep. commission  0.061714854 0.001323261   46.638460
## 22                    United Nations  0.024280174 0.001356516   17.898921
## 23                        Greenpeace -0.006573634 0.001377372   -4.772591
##                p        lower        upper
## 1             NA           NA           NA
## 2   0.000000e+00 -0.100593842 -0.095096727
## 3   0.000000e+00 -0.172886890 -0.167129978
## 4   0.000000e+00 -0.266654026 -0.260884521
## 5   0.000000e+00 -0.335644805 -0.330068886
## 6             NA           NA           NA
## 7   0.000000e+00  0.063296862  0.068552302
## 8   0.000000e+00  0.049843423  0.055116142
## 9   0.000000e+00  0.054678574  0.059882854
## 10            NA           NA           NA
## 11  0.000000e+00  0.090491569  0.094966332
## 12  0.000000e+00  0.154131988  0.158738218
## 13            NA           NA           NA
## 14  4.151128e-90  0.020308135  0.024689682
## 15  0.000000e+00  0.042967896  0.047380310
## 16            NA           NA           NA
## 17 5.616961e-105  0.025900360  0.031028137
## 18  2.200727e-44 -0.021132129 -0.015933874
## 19  0.000000e+00 -0.055752710 -0.050609216
## 20            NA           NA           NA
## 21  0.000000e+00  0.059121310  0.064308398
## 22  1.202281e-71  0.021621451  0.026938896
## 23  1.818711e-06 -0.009273234 -0.003874034
\end{verbatim}
\end{kframe}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
##      outcome statistic                                 feature
## 1  choice_cj        mm    Costs to average household per month
## 2  choice_cj        mm    Costs to average household per month
## 3  choice_cj        mm    Costs to average household per month
## 4  choice_cj        mm    Costs to average household per month
## 5  choice_cj        mm    Costs to average household per month
## 6  choice_cj        mm                   Distribution of costs
## 7  choice_cj        mm                   Distribution of costs
## 8  choice_cj        mm                   Distribution of costs
## 9  choice_cj        mm                   Distribution of costs
## 10 choice_cj        mm       Number of participating countries
## 11 choice_cj        mm       Number of participating countries
## 12 choice_cj        mm       Number of participating countries
## 13 choice_cj        mm   Share of global emissions represented
## 14 choice_cj        mm   Share of global emissions represented
## 15 choice_cj        mm   Share of global emissions represented
## 16 choice_cj        mm Sanctions for missing reduction targets
## 17 choice_cj        mm Sanctions for missing reduction targets
## 18 choice_cj        mm Sanctions for missing reduction targets
## 19 choice_cj        mm Sanctions for missing reduction targets
## 20 choice_cj        mm                           Monitoring by
## 21 choice_cj        mm                           Monitoring by
## 22 choice_cj        mm                           Monitoring by
## 23 choice_cj        mm                           Monitoring by
##                                level  estimate   std.error         z p
## 1                      \20028 per month 0.6729737 0.004126308 163.09342 0
## 2                      \20056 per month 0.5753704 0.004309124 133.52375 0
## 3                      \20084 per month 0.5028766 0.004395792 114.39955 0
## 4                     \200113 per month 0.4085284 0.004325220  94.45264 0
## 5                     \200141 per month 0.3394765 0.004148381  81.83349 0
## 6                          Only rich 0.4570055 0.003911228 116.84452 0
## 7         Prop. to current emissions 0.5216566 0.003926015 132.87176 0
## 8      Prop. to history of emissions 0.5087938 0.003917689 129.87090 0
## 9  Rich pay more than poor countries 0.5127165 0.003924942 130.63032 0
## 10                         20 of 192 0.4182276 0.003341616 125.15729 0
## 11                         80 of 192 0.5089863 0.003399306 149.73245 0
## 12                        160 of 192 0.5737857 0.003373566 170.08288 0
## 13          40% of current emissions 0.4781113 0.003380328 141.43933 0
## 14          60% of current emissions 0.4999291 0.003407780 146.70227 0
## 15          80% of current emissions 0.5222143 0.003402419 153.48325 0
## 16                              None 0.5106586 0.003932951 129.84109 0
## 17               \2006 per hh and month 0.5412417 0.003913371 138.30573 0
## 18              \20017 per hh and month 0.4928567 0.003908225 126.10754 0
## 19              \20023 per hh and month 0.4552868 0.003914718 116.30129 0
## 20                   Your government 0.4813399 0.003912654 123.02130 0
## 21                 Indep. commission 0.5426752 0.003901770 139.08437 0
## 22                    United Nations 0.5032115 0.003941043 127.68486 0
## 23                        Greenpeace 0.4725424 0.003920333 120.53630 0
##        lower     upper
## 1  0.6648863 0.6810611
## 2  0.5669247 0.5838161
## 3  0.4942610 0.5114922
## 4  0.4000512 0.4170057
## 5  0.3313459 0.3476072
## 6  0.4493397 0.4646714
## 7  0.5139617 0.5293514
## 8  0.5011153 0.5164723
## 9  0.5050237 0.5204092
## 10 0.4116781 0.4247770
## 11 0.5023238 0.5156488
## 12 0.5671737 0.5803978
## 13 0.4714860 0.4847366
## 14 0.4932500 0.5066083
## 15 0.5155456 0.5288829
## 16 0.5029502 0.5183671
## 17 0.5335716 0.5489118
## 18 0.4851967 0.5005167
## 19 0.4476140 0.4629595
## 20 0.4736712 0.4890085
## 21 0.5350279 0.5503225
## 22 0.4954872 0.5109358
## 23 0.4648587 0.4802262
\end{verbatim}
\end{kframe}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/bechtel_subgroup_mm-1} 
\begin{kframe}\begin{verbatim}
##                BY   outcome statistic
## 1          France choice_cj        mm
## 2          France choice_cj        mm
## 3          France choice_cj        mm
## 4          France choice_cj        mm
## 5          France choice_cj        mm
## 6          France choice_cj        mm
## 7          France choice_cj        mm
## 8          France choice_cj        mm
## 9          France choice_cj        mm
## 10         France choice_cj        mm
## 11         France choice_cj        mm
## 12         France choice_cj        mm
## 13         France choice_cj        mm
## 14         France choice_cj        mm
## 15         France choice_cj        mm
## 16         France choice_cj        mm
## 17         France choice_cj        mm
## 18         France choice_cj        mm
## 19         France choice_cj        mm
## 20         France choice_cj        mm
## 21         France choice_cj        mm
## 22         France choice_cj        mm
## 23         France choice_cj        mm
## 24        Germany choice_cj        mm
## 25        Germany choice_cj        mm
## 26        Germany choice_cj        mm
## 27        Germany choice_cj        mm
## 28        Germany choice_cj        mm
## 29        Germany choice_cj        mm
## 30        Germany choice_cj        mm
## 31        Germany choice_cj        mm
## 32        Germany choice_cj        mm
## 33        Germany choice_cj        mm
## 34        Germany choice_cj        mm
## 35        Germany choice_cj        mm
## 36        Germany choice_cj        mm
## 37        Germany choice_cj        mm
## 38        Germany choice_cj        mm
## 39        Germany choice_cj        mm
## 40        Germany choice_cj        mm
## 41        Germany choice_cj        mm
## 42        Germany choice_cj        mm

>>>>

\noindent These examples make clear that despite the \textit{causal} inference potentially provided by the AMCE, the quantity of interest is frequently used to provide a characterization of a preferences that has a distinctly descriptive flavor about the relative \textit{levels} of support across profiles and also across subgroups of respondents. Indeed, this style of description is widespread in conjoint analyses. This use of conjoints to provide descriptive inferences about patterns of preferences is important because AMCEs are defined as \textit{relative} quantities, requiring that patterns of preferences are expressed against a baseline, reference category for each conjoint feature. A positive AMCE is read as higher favorability but it is only higher relative to whatever category serves as the baseline. For example, in the \citeauthor{HainmuellerHopkinsYamamoto2014} candidate example, choosing a non-religious candidate as a baseline and interpreting the resulting AMCES means that the differences between other pairs of marginal means (e.g., evaluations of Mormon and Evangelical candidates) are not obvious. The negative direction, and the size, of the AMCEs for Mormon and Evangelical candidates would be different if the least-liked category of Mormons were the reference group. More trivially, \citet{TeeleKallaRosenbluth2018} describe their comparisons about public preferences for female candidates relative to male candidates, but could have equivalent described patterns of equal size but opposite sign comparing preferences over male relative to female candidates. Appendix \ref{app:referencecategory} includes some additional illustrations of this point for interested readers.

@@

To draw this example out more fully, the upper panel of Figure \ref{fig:tkr_replication} shows AMCEs for \citeauthor{TeeleKallaRosenbluth2018}'s candidate choice experiment for the full sample of respondents. The second panel shows full sample marginal means. Respondents' preference for female candidates is very apparent in both forms of analysis in the upper two panels because the AMCE definitionally equals the difference in marginal means. But how do Republicans and Democrats differ in their preferences over male and female candidates? The third panel shows conditional AMCEs separately for Democratic and Republican voters, as provided in the original paper and the lower panel shows the results using conditional marginal means for Democratic and Republican voters.\footnote{We opt here for visual presentation of results; tabular presentation of AMCEs, marginal means, and associated standard errors for all examples are included in the Appendix.} By requiring a reference category fixed to zero, the conditional AMCE results in the third panel suggest that there is a very large difference in favorability toward female candidates between Republican and Democratic respondents. In reality, however, the difference in these conditional AMCEs (0.089) reflects the true difference in favorability toward female candidates (difference: 0.045; Democrats: 0.537, Republicans: 0.492) \textit{plus} the difference in favorability toward male candidates (difference: 0.045; Democrats: 0.463, Republicans: 0.508). Because Democrats and Republicans actually differ in their views of profiles containing the reference (male) category, AMCEs sum the true differences in preferences for a given feature level with the difference in preferences toward the reference category.\footnote{Another example that clearly demonstrates the discrepancy between the differences in preferences and the differences in conditional AMCEs can be seen very clearly in the ``political experience'' feature of this experiment (see Appendix \ref{app:tkrpolexperience}).}

@@

\section{Impact of Reference Category Choice on AMCEs}\label{app:referencecategory}

Though seemingly arbitrary, the choice of reference category for estimating AMCEs can be quite consequential. For example, in \citeauthor{HainmuellerHopkinsYamamoto2014}'s candidate experiment (again, see \ref{fig:hainmueller_candidate_replication}), the least liked education level (``no formal education'') is chosen as a reference category, but the authors could have presented the results using any of the categories as the baseline.

The figure below shows how the estimated AMCEs for each level of the education feature would have differed depending on that choice. Selecting a reference category that receives middling support (i.e., more favorability than some other feature levels but less favorability than others), makes some AMCEs positive and others negative but all AMCEs can be made positive (or negative) simply by choosing a different baseline. The results would be numerically equivalent --- the alternative linear models used to the estimate the AMCEs have a mathematical equivalence --- but the choice has sizeable consequences for the interpretation of conjoint analyses, as we discuss below.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[h]
\includegraphics[width=\maxwidth]{figure/reference_category-1} \end{figure}

In \textit{constrained} conjoint designs, the choice of reference category is even more important. Consider, for example, the design of \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment, which constrains the ``Country of Origin`` feature so that levels `India,' `Germany,' `France,' `Mexico,' `Philippines,' and `Poland' cannot co-occur with the `Escape Persecution' level of the ``Reason for Application'' feature. Consequently, the AMCE for the ``Escape Persecution'' level (relative to the  ``Reunite with family'' reference category) is only defined for the subset of the design involving countries `China,' `Sudan,' `Somalia,' and `Iraq.' The AMCEs for those four countries (relative to India as a baseline) marginalize across all reasons for application, but the AMCEs for the first six countries marginalize only across the latter two reasons. Thus the interpretation of AMCEs --- and the basic ability to estimate them in constrained designs --- depends entirely upon the selection of a reference category where all feature levels can co-occur. In a design where \textit{all} features are constrained, then AMCEs are undefined for the design as a whole and only estimable for subsets of the design that are \textit{conditionally} unconstrained.

\section{Re-analysis of `Political Experience' Feature from Teele et al. (2018)}\label{app:tkrpolexperience}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/tkr_replication_experience-1}

\noindent Conditional AMCEs in this experiment (see 3rd panel, above) correctly convey that both Democrats and Republicans are more likely to favor experienced than inexperienced candidates. Reading the AMCEs descriptively, however, would suggest that Democratic voters are more favorable toward candidates with all levels of experience compared to Republican voters (i.e., Republicans and Democrats differ in their preferences over experienced candidates). Yet the conditional marginal means (4th panel, above) reveal that Democrats and Republicans have very similar preferences toward candidates with 1 or 3 years of experience, but differ dramatically in their preferences over candidates with no experience (the reference category) and those with 8 years experience. Democrats are much more sensitive to experience than are Republicans and important differences in preferences between the groups are apparent for very high and very low experience, but the conditional AMCEs suggest that preferences differ at all levels of experience, when in reality they do not.

@@

\subsection{Subgroup Analysis using AMCEs}

@@

\subsection{Subgroup Analysis using MMs}

@@

\subsection{Nested Model Comparison}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## Analysis of Deviance Table
## 
## Model 1: ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + 
##     Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + 
##     Education:Job + CountryOfOrigin:ReasonForApplication
## Model 2: ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + 
##     Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry + 
##     ethnocentrism_split + Education:Job + CountryOfOrigin:ReasonForApplication + 
##     Gender:ethnocentrism_split + Education:ethnocentrism_split + 
##     LanguageSkills:ethnocentrism_split + CountryOfOrigin:ethnocentrism_split + 
##     Job:ethnocentrism_split + JobExperience:ethnocentrism_split + 
##     JobPlans:ethnocentrism_split + ReasonForApplication:ethnocentrism_split + 
##     PriorEntry:ethnocentrism_split + Education:Job:ethnocentrism_split + 
##     CountryOfOrigin:ReasonForApplication:ethnocentrism_split
##   Resid. Df Resid. Dev Df Deviance     F Pr(>F)
## 1     11402     2500.7                         
## 2     11304     2475.8 98   24.834 1.157 0.1384
\end{verbatim}
\end{kframe}
\end{knitrout}
